Active Contextual Entropy Search

### 2016-05-27 2016_ICML/poster/content/left_column.tex
Updating title/abstract and some pics

\begin{block}{\blocktitle{Abstract}}
\justifying
Contextual policy search allows adapting robotic movement primitives to
different situations. For instance, a locomotion primitive might be adapted to
different terrain inclinations or desired walking speeds. Such an adaptation
is often achievable by modifying a small number of hyperparameters.
However, learning, when performed on real robotic systems, is typically
restricted to a small number of trials. Bayesian optimization
has recently been proposed as a sample-efficient means for contextual policy search
that is well suited under these conditions.
In this work, we extend entropy search, a variant of Bayesian optimization,
such that it can be used for \emph{active} contextual policy search where the agent
selects those tasks during training in which it expects to learn the most.
\end{block}

@@

\begin{block}{\blocktitle{Illustration}}
\vspace*{1cm}
%\includegraphics[width=.99\columnwidth]{../pics/aces.pdf}

>>>>

\begin{block}{\blocktitle{Abstract}}
\justifying
We propose minimum regret search (MRS), a novel acquisition function for Bayesian
optimization. MRS bears similarities with information-theoretic approaches
such as entropy search (ES). However, while ES aims in each query at maximizing the
information gain with respect to the global maximum, MRS aims at minimizing the
expected simple regret of its ultimate recommendation for the optimum. While empirically ES and MRS perform similar in most of the
cases, MRS produces fewer outliers with high simple regret than ES. We provide empirical
results both for a synthetic single-task optimization problem as well as for a
simulated multi-task robotic control problem.
\end{block}

@@

\begin{block}{\blocktitle{Illustration}}
\vspace*{1cm}

\begin{figure}
\centering
\includegraphics[width=0.4\columnwidth]{../pics/regret_illustration}
\includegraphics[width=0.4\columnwidth]{../pics/acq_comparison}
\caption{(Left) Illustration of GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on the right-hand side). (Right) Illustration of GP posterior and different acquisition function. Absolute values have been normalized such that the mean value of an acquisition function is $0.5$. Best seen in color.}
\label{fig:MRS_illustration}
\end{figure}

### 2016-05-27 2016_ICML/poster/content/right_column.tex
Updating title/abstract and some pics

\begin{figure}
\centering
%\includegraphics[width=0.3\textwidth,clip=true,trim=200 120 250 100]{pics/compi}
%\includegraphics[width=0.58\textwidth]{../pics/learning_curve}
%\includegraphics[width=0.4\textwidth]{../pics/context_selection}
\caption{(Left) Learning curves on the simulated robot arm COMPI: the offline performance is evaluated each 10 episodes on 16 test contexts distributed on a grid over the target area. Mean and its standard error over 20 independent runs. (Right) Scatter plot showing the sampled contexts for all (blue) and a single representative run (red).}
\label{fig:experiment}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=.9\columnwidth]{../pics/empirical_comparison} \\
\includegraphics[width=.9\columnwidth]{../pics/hist}
\caption{(Top) Median and mean simple regret over $250$ repetitions for different acquisition functions. Shown is the simple regret of the recommendation $\mathbf{\tilde x}_N$ after $N$ trials, i.e., the point which maximizes the GP posterior
mean. (Bottom) Histogram of the simple regret after performing $N=100$ trials for different acquisition functions (note the log-scales).}
\label{fig:empirical_comparison}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\textwidth]{../pics/es_analysis}
\caption{Illustration of acquisition functions on a target function for
100 given samples and 25 representer points; darker areas correspond to larger values. ES focuses on sampling in areas with high density of $p^\star$ (many representer points), while MRS focuses on unexplored areas that are populated by representer points (non-zero $p^\star$).
}
\label{fig:es_analysis}
\end{figure}

### 2016-05-27 2016_ICML/poster/defines/header.tex
Updating title/abstract and some pics

\setbeamertemplate{headline}
{%
  \setbeamercolor{mycolor}{fg=black,bg=white}
   \begin{beamercolorbox}{mycolor}
    \centering{\parbox{70cm}{\centering{\huge{\textbf{\inserttitle}}}}}\\[5mm]
    \centering{\parbox{70cm}{\centering{\Large{\insertauthor\\[.5cm] University Bremen,
Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen,
Germany\hspace{2cm}}}}}

>>>>

\setbeamertemplate{headline}
{%
  \setbeamercolor{mycolor}{fg=black,bg=white}
   \begin{beamercolorbox}{mycolor}
    \centering{\parbox{70cm}{\centering{\huge{\textbf{\inserttitle}}}}}\\[5mm]
    \centering{\parbox{70cm}{\centering{\Large{\insertauthor\\[.5cm] University Bremen,
Robotics Research Group, Robert-Hooke-Str.~1, 28359 Bremen, Germany\\
Corporate Research CR/AEY2, Robert Bosch GmbH, 70442 Stuttgart, Germany
}}}}
